---
title: "MCMC Diagnostic Appendix"
author: "Bayesian AR(p) Engine"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(bayesplot)
library(ggplot2)
```

# Executive Summary

This appendix provides the diagnostic verification for the Bayesian AR(p) model fit. We assess chain convergence, mixing efficiency, and parameter recovery against the ground truth.

## Statistical Summary

```{r summary_table}
# The 'params_summary' object should be passed from the environment
if (exists("params_summary")) {
  knitr::kable(params_summary, digits = 3, caption = "Posterior Summary Statistics")
} else {
  cat("Summary statistics not available.")
}
```

# Parameter Diagnostics

```{r diagnostics_loop, results='asis'}
# The 'plot_list' object should be passed from the environment
if (exists("plot_list")) {
  for (p_name in names(plot_list)) {
    cat("\n## Parameter:", p_name, "\n")

    # Trace Plot
    print(plot_list[[p_name]]$trace)
    cat("\n\n")

    # Density Plot
    print(plot_list[[p_name]]$density)
    cat("\n\n")

    # ACF Plot
    print(plot_list[[p_name]]$acf)
    cat("\n\n")

    # Rank Plot
    print(plot_list[[p_name]]$rank)
    cat("\n\n")
  }
} else {
  cat("No plots found in the list.")
}
```

\newpage

# Glossary

- **ESS (Effective Sample Size):** Number of independent draws equivalent to the total samples.
- **95% HPD (Highest Posterior Density):** The narrowest interval containing 95% of the posterior mass.
- **Trace Plots:** Used to visually inspect convergence and mixing.
- **Rank Histograms:** Used to verify uniform exploration of the posterior logic.
